### 2011-01-02 docs/slides/mimicry.tex
Evolutionary Dynamics section added to slides.

\section{The Inspiration: Mimicry}

@@

\frame
{
	\frametitle{Evolutionary Dynamics}
}

\subsubsection{Mimicry Rings}

\frame
{
	\frametitle{Mimicry Rings}
}

>>>>

\section{The Inspiration}

@@

\frame
{
	\frametitle{Evolutionary Dynamics}
	\framesubtitle{Punctuated Equilibrium}

	Explanation for evolutionary dynamics of mimicry is from Turner. Most sexually reproducing species will remain:
	\begin{itemize}
		\item in extended state of \textit{stasis}.
		\item Little evolutionary change in most of their geological history.
	\end{itemize}

	Cladogenesis:
	\begin{itemize}
		\item Process of speciation.
		\item One species split into two distinct species.
		\item It is a discontinuous change, rather than a gradual transformation in a geological time.
	\end{itemize}
}

\frame
{
	\frametitle{Evolutionary Dynamics}
	\framesubtitle{Phyletic Gradualism}

	\begin{itemize}
		\item Species continue to adapt to new environmental and biological selection pressure.
		\item Gradually becomes a new species.
	\end{itemize}

	Phyletic gradualism holds that,
	\begin{itemize}
		\item Species population changes gradually.
		\item There is no clear demarcation between an ancestral species and a descendant species.
		\item Gradually changing lineage is divided arbitrarily.
		\item Evolution is 
			\begin{itemize}
				\item smooth
				\item steady
				\item incremental
				\item but not necessary constant and slow rate in geological time scale.
			\end{itemize}
	\end{itemize}
}

\frame
{
	\frametitle{Evolutionary Dynamics}
	\framesubtitle{Punctuated Equilibrium vs. Phyletic Gradualism}

	\begin{figure}[H]
		\centering
		\includegraphics[scale=0.3]{../tex/images/Punctuated-equilibrium}
		\caption{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism. Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
		\label{fig:punctuated-equilibrium}
	\end{figure}
}

\frame
{
	\frametitle{Evolutionary Dynamics}
	\framesubtitle{Turner's Two Stage Model}

	\begin{itemize}
		\item Turner came up with a synthetic theory.
		\item Theory originated from Poulton and Nicholson.
		\item Mimicry arises in two steps:
			\begin{enumerate}
				\item A comparatively large mutation achieves a good approximate resemblance.
				\item A gradual evolutionary change refines the resemblance to a higher degree of perfection.
			\end{enumerate}
		\item This theory has also been applied to Mullerian Mimicry.
	\end{itemize}
}

\subsubsection{Mimicry Ring}

\frame
{
	\frametitle{Mimicry Ring}

	\begin{itemize}
		\item 
	\end{itemize}	
}

\frame
{
	\frametitle{Mimicry Ring}
	\framesubtitle{Formation}

	\begin{itemize}
		\item 
	\end{itemize}
}
